Maximising the Guaranteed Feasible Set for Uncertain MPC Schemes with Probabilistic Constraints

### 2016-11-04 tmp.tex
edits 1
various edits (more to follow)

\section{Introduction}
%
%
Determining positive invariant sets for uncertain linear systems has been discussed in the literature for decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
%
Properties of such sets and the algorithms to compute them have are known and documented in the literature.
%
In addition to pure analysis purposes, these sets are often used as terminal constraint sets in model predictive control formulations in order to guarantee the feasibility of the control scheme at all times, see e.g.~\cite{Mayne2014}.
%
To be able to apply the methods presented in~\cite{Kolmanovsky:1998} and~\cite{blanchini:2007} the modelled uncertainty has to be constrained to known convex set, in particular a polytope or a ellipsoid.
%
If constraints on the system do not have to be satisfied for all possible uncertainties but merely for a subset then the problem becomes a chance constrained problem, see e.g.~\cite{Kall2010}.
%
Control formulations of this kind can be addressed using a range of techniques including scenario optimization, see e.g.~\cite{Calafiore2010}, and sampling based methods, e.g.~\cite{Margellos2014,Zhang2015}.
%
However, the sets determined based on sampled uncertainties are computationally expensive to obtain and guaranties can only be given in a stochastic sense, i.e. with a certain confidence level.
%
The method presented in~\cite{Zhang2015} is based on determining a certain set in which the probabilistic requirements are met with a given confidence and using that set for subsequent analysis.
%
This concept does not require sampling for simple probability distributions, instead we can explicitly parametrise an auxiliary set in which all probabilistic conditions are met.
%
Using such a parametrised set, we can optimise the size of the positive invariant set for the particular set in order to produce the largest positive invariant set while guaranteeing satisfaction of the probabilistic constraints, hence approximating the positive invariant set of the original problem.
%
Unlike sample based approaches this method inherently guarantees probabilistic constraint satisfaction.

>>>>

\section{Introduction}
%
%
Positively invariant sets for uncertain linear systems have been researched for several decades, see e.g.~\cite{Kolmanovsky:1995,Kolmanovsky:1998,blanchini:2007}.
%
The properties of such sets and the algorithms to compute them are well known and documented in the literature.
%
As well as being objects of interest in their own right,
%In addition to pure analysis purposes, 
these sets are often used as terminal constraint sets in model predictive control formulations, since in order to guarantee the feasibility of the control scheme at all times, see e.g.~\cite{Mayne2014}.
%
To be able to apply the methods presented in~\cite{Kolmanovsky:1998} and~\cite{blanchini:2007} the modelled uncertainty has to be constrained to known convex set, in particular a polytope or a ellipsoid.
%
If constraints on the system do not have to be satisfied for all possible uncertainties but merely for a subset then the problem becomes a chance constrained problem, see e.g.~\cite{Kall2010}.
%
Control formulations of this kind can be addressed using a range of techniques including scenario optimization, see e.g.~\cite{Calafiore2010}, and sampling based methods, e.g.~\cite{Margellos2014,Zhang2015}.
%
However, the sets determined based on sampled uncertainties are computationally expensive to obtain and guaranties can only be given in a stochastic sense, i.e. with a certain confidence level.
%
The method presented in~\cite{Zhang2015} is based on determining a certain set in which the probabilistic requirements are met with a given confidence and using that set for subsequent analysis.
%
This concept does not require sampling for simple probability distributions, instead we can explicitly parametrise an auxiliary set in which all probabilistic conditions are met.
%
Using such a parametrised set, we can optimise the size of the positive invariant set for the particular set in order to produce the largest positive invariant set while guaranteeing satisfaction of the probabilistic constraints, hence approximating the positive invariant set of the original problem.
%
Unlike sample based approaches this method inherently guarantees probabilistic constraint satisfaction.
